Observed vs. Simulated Year Comparison

### 2023-06-28 03-post-process/ms-content/ms-content.Rmd
Create the "no fall" figure

@@

>>>>

no_fall_caption = "
  Ratios between the across-year mean (dark grey) and coefficient of variation (light grey) abundance of natural-origin smolt reaching Lower Granite Dam with (denominator) and without (numerator) the fall migrant life history strategy.
  The 'without' scenario was calculated by assuming all parr recruits experienced freshwater survival rates of spring migrants.
  Mean ratios <1 and CV ratios >1 indicate LGR smolt abundance would be lower and more variable, respectively, in the absence of the fall migrant strategy.
  Values presented are posterior means and 95% credible regions.
"
```

@@

```{r no-fall-fig, fig.width = 3.4, fig.height = 3.4, fig.cap = msdown::prep_caption(no_fall_caption), time_it = TRUE}
cv = function(x) {sd(x, na.rm = TRUE)/mean(x, na.rm = TRUE)}

##### STEP 1: EXTRACT POSTERIOR SAMPLES OF QUANTITIES NEEDED #####

# total parr recruitment (regardless of LH type)
Pb = post_subset(post, "^Pb[", matrix = TRUE)

# total smolt at LGR (separated by LH type)
Ma = post_subset(post, "^Ma[", matrix = TRUE)

# overwinter survival (separated by LH type)
phi_Pa_Mb = post_subset(post, "^phi_Pa_Mb[", matrix = TRUE)

# migration survival (separated by LH type, but assumed constant)
phi_Mb_Ma = post_subset(post, "^phi_Mb_Ma[", matrix = TRUE)

##### STEP 2: DEFINE A FUNCTION TO CALCULATE THE DESIRED STATS FOR A GIVEN POSTERIOR SAMPLE #####
f = function(i) {
  # put the values from this draw into the format used in the model
  Pb_i = array_format(Pb[i,])
  Ma_i = array_format(Ma[i,])
  phi_Pa_Mb_i = array_format(phi_Pa_Mb[i,])[,i_spring,]
  phi_Mb_Ma_i = array_format(phi_Mb_Ma[i,])[,i_spring,o_nor,]

  # calculate hypothetical NOR smolt reaching LGR if all parr were spring migrants
  Ma_tot_hyp_i = Pb_i * phi_Pa_Mb_i * phi_Mb_Ma_i

  # calculate actual NOR smolt reaching LGR
  Ma_tot_real_i = Ma_i[,i_fall,o_nor,] + Ma_i[,i_spring,o_nor,]

  # add columns storing the aggregate across populations
  Ma_tot_hyp_i = cbind(Ma_tot_hyp_i, rowSums(Ma_tot_hyp_i))
  Ma_tot_real_i = cbind(Ma_tot_real_i, rowSums(Ma_tot_real_i))

  # calculate the ratios between the actual and hypothetical
  mean_p_ratio = colMeans(Ma_tot_hyp_i/Ma_tot_real_i, na.rm = TRUE)
  cv_ratio = apply(Ma_tot_hyp_i, 2, cv)/apply(Ma_tot_real_i, 2, cv)

  names(mean_p_ratio) = paste0("mean_p_ratio[", 1:5, "]")
  names(cv_ratio) = paste0("cv_ratio[", 1:5, "]")
  c(mean_p_ratio, cv_ratio)
}

##### STEP 3: APPLY FUNCTION TO ALL POSTERIOR SAMPLES, FORMAT, AND SUMMARIZE #####

# apply
ratio_out = t(sapply(1:nrow(Pb), f))

# format
ratio_post = post_convert(cbind(postpack:::id_mat(post), ratio_out))

# summarize
mean_summ = post_summ(ratio_post, "mean")
cv_summ = post_summ(ratio_post, "cv")

# format the summaries for barplotting
mns = rbind(mean_summ["mean",], cv_summ["mean",])
lwrs = rbind(mean_summ["2.5%",], cv_summ["2.5%",])
uprs = rbind(mean_summ["97.5%",], cv_summ["97.5%",])

# set the colors
cols = c("grey50", "grey80")

# make the plot
mypar(mfrow = c(1,1), col.axis = "black")
mp = barplot(mns, beside = TRUE, names.arg = c(pops, "TOTAL"),
             ylim = c(0, 1.35), border = NA, col = cols)

# draw error bars
segments(mp, lwrs, mp, uprs)

# draw x-axis
segments(par("usr")[1], par("usr")[3], par("usr")[2], par("usr")[3], xpd = TRUE, col = par("col.axis"))
axis_labels("Population", "Without:With Fall Migrant Strategy")

# draw a reference line
abline(h = 1, lty = 2)

# draw a legend
legend("topright", title = "LGR Smolt", legend = c("Mean", "CV"), pch = 15,
       col = cols, pt.cex = 1.5, bty = "n", text.col = par("col.axis"), cex = 0.8)
```

  row_spec(0, bold = TRUE) %>%
  column_spec(1, monospace = TRUE) %>%
  row_spec(nrow(tab), bold = TRUE)
```
